No Replication Without Process Documentation:  An Assessment of Management

### 2020-04-06 R/MSE manuscript.Rmd
Covert markdown table of MSE counts to kable table produced with R code.

# Methods 
## Finding and Sampling the MSE Literature 
We conducted our search for MSEs in the SCI-EXPANDED index from Web of Science, searching for “management strategy evaluation” by topic across all years on January 8th, 2019 (Table 1). This search returned 264 results.  We reviewed a random sample of 30 articles that document a MSE (supplement 2), removing articles that were reviews, meta-analyses, or simply cited other MSE articles from our sample. After removing other articles from the original set of 264 articles, 154 articles document a MSE.  We reviewed 16 climate change MSE articles (supplement 2). Twelve of these articles came from our original January 8th, 2019 Web of Science search.  To give as full a picture of the climate change MSE articles to date as possible we also reviewed the 4 climate change MSE articles published in 2019.

Table 1. Januaray 8, 2019 Web of Science "management strategy evaluation" search results
| MSE type | Count |
|:--:|:--:|
| Published | 154 |
| Random Sample | 30 |
| Climate Change | 12* |  
* We also reviewed 4 additional climate change MSE articles published in 2019 for a total of 16.

@@

```{r, SDMfigure, fig.cap='Review framework - structured decision making process'}
knitr::include_graphics('figs/SDMProcessFramework.png')
```

>>>>

# Methods 
## Finding and Sampling the MSE Literature 
We conducted our search for MSEs in the SCI-EXPANDED index from Web of Science, searching for “management strategy evaluation” by topic across all years on January 8th, 2019 (Table \@ref(tab:MSEcount)). This search returned 264 results.  We reviewed a random sample of 30 articles that document a MSE (supplement 2), removing articles that were reviews, meta-analyses, or simply cited other MSE articles from our sample. After removing other articles from the original set of 264 articles, 154 articles document a MSE.  We reviewed 16 climate change MSE articles (supplement 2). Twelve of these articles came from our original January 8th, 2019 Web of Science search.  To give as full a picture of the climate change MSE articles to date as possible we also reviewed the 4 climate change MSE articles published in 2019.

```{r MSEcount}
MSE_Type<-c("Published","Random Sample","Climate Change")
Count<-c(154,30,"12*")
Table1.data<-as_tibble(cbind(MSE_Type,Count))
  Table1.data %>%
    rename("MSE Type"=MSE_Type) %>% 
  kable(caption = "Januaray 8, 2019 Web of Science 'management strategy evaluation' search results") %>% 
  kable_styling() %>% 
    add_footnote(c("We also reviewed 4 additional climate change MSE articles published in 2019 for a total of 16."), notation = "symbol")
```

@@

```{r, SDMfigure, fig.cap='Review framework - structured decision making process'}
knitr::include_graphics(here('figs/SDMProcessFramework.png'))
```
